FictionEro - Data Cleaning

### 2024-02-04 analysis/1_cleaning.qmd
fix comments

```{r}
data.frame(Language = df$Language,
           Source = df$Experimenter,
           Comments = trimws(df$Feedback_Comments)) |> 
  filter(!Comments %in% c("", "No", "Nope", "nope", "None", "na")) |> 
  arrange(Language, Source) |>
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```

@@

<!-- ## Ethnicity -->

<!-- ```{r p_demographics_ethnicity} -->
<!-- plot_waffle <- function(sub, what = "Nationality", title = what, rows = 8, size = 3) { -->
<!--   ggwaffle::waffle_iron(sub, what, rows = rows) |> -->
<!--     ggplot(aes(x, y)) + -->
<!--     geom_point(aes(color = group), shape = "square", size = size) + -->
<!--     coord_equal() + -->
<!--     ggtitle(title) + -->
<!--     labs(fill = "", color = "", subtitle = "N participants per self-declared group") + # (each square represents one participant)" -->
<!--     theme_void() + -->
<!--     theme( -->
<!--       plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0), -->
<!--       plot.subtitle = element_text(size = rel(1.2)), -->
<!--       legend.key.height = unit(1, "mm"), -->
<!--       legend.key.width = unit(1, "mm") -->
<!--     ) -->
<!-- } -->

<!-- p_ethni <- plot_waffle(sub, "Ethnicity", rows = 20, size = 8) + -->
<!--   scale_color_manual(values = c("Hispanic" = "#FF5722", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Asian" = "#FFC107", "Other" = "#795548")) -->
<!-- p_ethni -->
<!-- ``` -->

>>>>

```{r}
data.frame(Language = df$Language,
           Source = df$Experimenter,
           Comments = trimws(df$Feedback_Comments)) |> 
  filter(!Comments %in% c(NA, "", "No", "Nope", "nope", "None", "na")) |> 
  arrange(Language, Source) |>
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```

@@
